\section{Methodology}

We investigate persona-persona dislike through a two-pronged approach: (1) measuring the correlation between persona distance and preference devaluation, and (2) testing for \schismogenesis.

\subsection{Persona Selection and Distance Mapping}

We sample 20 multifaceted personas from the \dataset dataset. Each persona includes a summary, cultural background, and professional bio. To quantify the "social distance" between personas, we compute embeddings for the full descriptions using the \embeddingmodel model. We define the distance $d(P_A, P_B)$ between Persona $A$ and Persona $B$ as the cosine distance between their respective embeddings:
\begin{equation}
    d(P_A, P_B) = 1 - \frac{\vv_A \cdot \vv_B}{\|\vv_A\| \|\vv_B\|}
\end{equation}
where $\vv_A$ and $\vv_B$ are the embedding vectors.

\subsection{Preference Generation and Reciprocal Evaluation}

For each persona, we use \gpt to generate 5 specific "likes" and 5 specific "dislikes" based on their description. These preferences are intended to be grounded in their lifestyle and values.

In the evaluation phase, we select 10 personas to act as "Evaluators." Each Evaluator is prompted to adopt their assigned persona and rate their agreement with the preferences of 6 target personas on a 1--5 Likert scale. The targets are selected to cover a range of distances:
\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=0pt]
    \item {\bf Self:} The Evaluator's own preferences (baseline).
    \item {\bf Close:} Two target personas with small $d(P_A, P_B)$.
    \item {\bf Medium:} One target persona with moderate distance.
    \item {\bf Far:} Two target personas with maximum distance in the sampled set.
\end{itemize}

\subsection{\Schismogenesis Test}

To test if LLMs capture the structural logic of opposition, we conduct a "zero-shot schismogenesis" test. The model is instructed: "You are the complete opposite of [Target Persona Description]. Rate your agreement with the following preferences of [Target Persona]." We measure the rejection rate (percentage of ratings $\le 2$) and the average Likert score.

\subsection{Metrics}

We evaluate the relationship between distance and dislike using:
\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=0pt]
    \item {\bf Pearson $r$ and Spearman $\rho$:} Correlation between $d(P_A, P_B)$ and average Likert rating.
    \item {\bf Rejection Rate:} Frequency of negative ratings (1 or 2) in cross-persona and schismogenesis tasks.
    \item {\bf Qualitative Justification:} Analysis of the reasoning provided by the model for its ratings.
\end{itemize}
